Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-09 WRITEUP/ms.tex
polish a bit up to sec 3.3

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local universe and at the peak epoch of cosmic \SF.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA and the ngVLA 
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn 
affect the regulation of thermal and chemical structures of their ISM. 
Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
are therefore expected to differ from nearby galaxies.
Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been 
observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
It is thus obvious and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
at the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.

@@

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
	Star formation history of \flower (top right) and
	projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter ``virial radius'' at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see calculation presented by \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

\section{Results}     \label{sec:results}

\subsection{Cloud Scaling Relations}

@@

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
the ``cloud'' mass ($M_{\rm cl}$),
the ``cloud'' size ($R$),
the Mach number ($\mathcal{M}$),
the velocity dispersion ($\sigma$), and the
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
\end{equation}
where $N$ is the number of zones of each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
We find comparable velocity dispersion derived by taking the root mean square versus
that derived using thermal and non-thermal pressure, indicating that
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
We quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
$M_*$)).
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{
Distributions of masses, sizes, and gas mass fractions of MCs identified using 
the lowest $n_{\rm cut}$ (left panels) and the highest $n_{\rm ncut}$ (right panels).
Note the y-axis scales are different between the left and the right panels, as less MCs are identified 
at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

In the following subsections,
we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
describe interactions between gravity and turbulence and is the first set of 
relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
density-size, and mass-size relations) and for comparing properties of molecular structures
in different galactic environments.
% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
Observations of nearby gas-rich galaxies such as M64 and NGC\,253
show higher velocity dispersions compared
to the disk/mid-plane of the Milky Way which
are more consistent with those observed in the inner regions of
Milky Way \citep{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}.  % also higher $P_{\rm int}$,
% which is $\propto\rho\sigma^2$
While the velocity dispersions of the clouds in these nearby gas-rich galaxies are comparable
to the inner regions of Milky Way, they are found to be bigger in size (approximately
an order of magnitude) and mass (approximately two orders of magnitude).
These bigger clouds have been interpreted as a results of their higher gas mass fractions and
surface densities and velocity dispersions, since
fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$
and Jeans mass $M_J\propto\sigma^4/\Sigma$
for dispersion-supported structures.

\subsubsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to the scaling in one of the Larson's relations (linewidth-size)
and can be re-written in the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

\subsubsection{Single Snapshots}  \label{sec:singless}

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (they also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound, and is supported/confined 
by turbulence and rotation on large scales.
% clouds form in galactic disk typically have virial between 0.2-10 \citep{Dobbs08a, Tasker09a}.

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC found in the arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies 
since the cosmic dark ages.
Current consensus is that at higher redshifts, galaxies have higher 
star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
Since their metallicity and dust content are also expected to be lower as they are assembling, 
this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn 
affect the regulation of thermal and chemical structures of their ISM. 
Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
are therefore expected to differ from nearby galaxies.
Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been 
observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
It is thus intuitive and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
%

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, spatially resolved ISM properties of \highz galaxies
have only been examine observationally in a handful of (strongly-lensed)
galaxies, using tracers such as
dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
the epoch of reionization  ---
which is responsible for producing the
ionizing photons that reionized the Universe.

@@

\begin{figure*}[!hHtbp]
\centering
\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
	Star formation history of \flower (top right) and
	projected stellar mass distribution of \flower during one of its accretion phases
	at its early stage of evolution {\it (a)}; during one of its major starburst phases
	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

@@

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
the critical density of the Universe % presumably defined at the redshift of \flower here?
is $r_{\rm 200}$\ssim15\,kpc.}.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
where ``clumps/structures'' are 
found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see Appendix of \citealt{Pallottini17b}).
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no qualitative differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

\section{Results: Cloud Scaling Relations}     \label{sec:results}

@@

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
mass ($M_{\rm cl}$),
size ($R$),
Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and 
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
\end{equation}
where $N$ is the number of zones of each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as 
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{
Distributions of masses, sizes, and gas mass fractions of MCs identified using 
the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
Note the scale shown on the y-axes are different between the left and right panels, as less MCs are identified 
at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

In the following subsections,
we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
describe interactions between gravity and turbulence and is the first set of 
relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
density-size, and mass-size relations) and for comparing properties of molecular structures
in different galactic environments.
% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
Observations of nearby gas-rich galaxies such as M64 and NGC\,253
show higher velocity dispersions compared
to the disk/mid-plane of the Milky Way which are, on the other hand,
more consistent with those observed in the inner regions of
Milky Way \citep{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}.  % also higher $P_{\rm int}$,
% which is $\propto\rho\sigma^2$
While the velocity dispersions of the clouds in these nearby gas-rich galaxies are comparable
to the inner regions of Milky Way, they are found to be bigger in size (approximately
an order of magnitude) and mass (approximately two orders of magnitude).
These bigger clouds have been interpreted as a results of their higher gas mass fractions and
surface densities and velocity dispersions, since
fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$
and Jeans mass $M_J\propto\sigma^4/\Sigma$
for dispersion-supported structures.

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:virial}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

\subsection{Single Snapshots}  \label{sec:singless}

@@

In each snapshot (see \Fig{MC} for example),
we identify a set of MCs with consistently high turbulences and surface densities
regardless of the H$_2$ density cuts adopted.
These are the MCs at the center of the main disk of \flower and
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
\AP{however a plot showing the clump stats has not been show yet at this point}
Their high velocity dispersions and surface densities are expected since
they are located in the nuclear regions of the
galaxy, where the potential well is also deeper. The higher velocity dispersions
in these MCs can also be understood as they have experienced more recent episodes
of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales.
% clouds form in galactic disk typically have virial between 0.2-10 \citep{Dobbs08a, Tasker09a}.

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$
are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.
